An algorithm for searching the global minimum of univariate discontinuous functions\thanks{This work was supported by project no. 0729-2020-0055.}

### 2020-12-14 2021/ICCS_BarkalovUsova/iccs.tex
Added bibliography, formules, figures and tables

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}

%%%% ДЛЯ РУССКОГО ТЕКСТА
%\usepackage[utf8x]{inputenc}
%\usepackage[english,russian]{babel}
%\usepackage{cmap}
%%%%

@@

\keywords{Global optimization \and Multiextremal functions \and 
Dimensionality reduction \and Peano curve \and Nested optimization \and 
Numerical methods.}
\end{abstract}
%
%
%
\section{Introduction}

\section{The global search algorithm}
\label{SectionCore}

\section{Results of numerical experiments}

Example of references 
The comparison of the algorithms has been carried out using the Grishagin test problems $F_{gr}$ (see, for example, \cite{Grishagin1994}, test function 4) and the GKLS generator \cite{Gaviano2003}.
In \cite{Barkalov2015,Grishagin2018} the global search algorithm (GSA) with the use of the evolvents as well as in combination 
with the adaptive dimensionality reduction scheme was shown to overcome many well known optimization 
algorithms including DIRECT \cite{Jones1993} and DIRECT\textit{l} \cite{Gablonsky2001}. Therefore, in the present study we will limit ourselves to the comparison of the  variants of GSA with different dimensionality reduction schemes.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{amsmath,amssymb}
\usepackage{mathtext}

\newcommand{\sign}{\operatorname{sign}}

%%%% ДЛЯ РУССКОГО ТЕКСТА закомментировать потом!
%\usepackage[utf8x]{inputenc}
%\usepackage[english,russian]{babel}
%\usepackage{cmap}
%%%%

@@

\keywords{Global optimization \and Multiextremal functions \and 
Dimensionality reduction \and Peano curve \and Nested optimization \and 
Numerical methods.}

\end{abstract}
%
%
%
\section{Introduction}

$x^*$

$\varphi(x)$

\begin{equation}\label{problem}
\varphi(x^*)=\min\left\{\varphi(x):x\in\left[a,b\right]\right\}.
\end{equation}

(see, for example, popular approaches in \cite{Sergeyev2013}, \cite{PaulaviciusZilinskas2014}, \cite{Sergeyev2017}).

(\ref{problem})

\cite{Horst1995}, \cite{Horst1996}, \cite{Pinter1996})

$\varphi(x)$

$\varphi(x)$  $L$

\[
\left|\varphi(x')-\varphi(x'')\right|\leq L\left|x'-x''\right|,\; x',x'' \in [a,b].
\]

\cite{Jones2009}, \cite{Evtushenko2009}, \cite{Paulavicius2011}, \cite{Evtushenko2013}.

\begin{itemize}
  \item
  \item 
  \item
\end{itemize}

\cite{Moreau2000}, \cite{Batukhtin1993}, \cite{Batukhtin1998}
\cite{Ban2019}, \cite{ZhangXu}

\cite{Strongin2000}

 MATLAB Global Optimization Toolbox \cite{MatlabOTB}. Section 6 concludes the paper.

\section{2}

(\ref{problem})

objective function $\varphi(x):x\in[a,b]$

\begin{equation}\label{points}
a = \omega_0 <\omega_1 < ... <\omega_s < \omega_{s+1} = b.
\end{equation}

\begin{equation}\label{LipschitzСondition}
\left|\varphi(x')-\varphi(x'')\right|\leq L\left|x'-x''\right|,\; x',x'' \in (\omega_{i-1},\omega_{i}), 1 \leq i \leq s+1.
\end{equation}

$\omega_{0}$ and $\omega_{s+1}$

$\Omega$ $\Omega = \{\omega_{0}, ..., \omega_{s+1}\} \omega_{0} = a, \omega_{s+1} = b$

\cite{Strongin2000}

$s+1$

$x^i \in (\omega_{i-1},\omega_{i}), 1 \leq i \leq s+1 $

$x^{k+1}$, $k \geq s+1$

$x^1,…,x^k$

$\omega_{0}, ..., \omega_{s+1}$

$x_i, 0\leq i \leq m = k + s + 1$

\begin{equation}\label{pointsX}
a = x_0 < x_1 < ... < x_{m-1} < x_{m} = b,
\end{equation}

$z_i=\varphi(x_i)$

$x_i \not\in \Omega$

$(x_{i-1},x_i )$

$(x_{i-1},x_i ), 1\leq i \leq m$

\begin{equation}\label{mu_i}
\mu_i=(1-\gamma_i-\gamma_{i-1} )  \frac{|z_i-z_{i-1} |}{(x_i-x_{i-1} )}
\end{equation}

\begin{equation}\label{gamma}
\gamma_i = 
\begin{cases}
	1, &\text{$x_i \in \{\omega_{0},...,\omega_{s+1}\} $} \\
	0, &\text{$x_i \not\in \{\omega_{0},...,\omega_{s+1}\} $}
\end{cases}
\end{equation}

\begin{equation}\label{mu}
\mu=\max\left\{\mu_i: 1 \leq i \leq m\}\right\}
\end{equation}

$\mu=0$ $\mu=1$

$ 0 \leq \gamma_i+\gamma_{i-1} \leq 1$

$ 1 \leq i \leq m$

 $\mu_i$

 $0$

$ (x_{i-1},x_i ),1 \leq i \leq m$

$\Omega$

$(x_{i-1},x_i ), 1\leq i \leq m$

\begin{equation}\label{R_i}
R(i)=(1+\gamma_i+\gamma_{i-1} )\Delta_i+(1-\gamma_i-\gamma_{i-1} ) \frac{ (z_i-z_{i-1} )^2}{(r\mu)^2 \Delta_i }  -\frac{2[(1-\gamma_i )(1+\gamma_{i-1} ) z_i+(1+\gamma_i )(1-\gamma_{i-1} ) z_{i-1} ]}{r\mu}
\end{equation}

$r>1$

\begin{equation}\label{R}
R(t)=\max\left\{R(i): 1 \leq i \leq m\}\right\}
\end{equation}

\begin{equation}\label{new_x}
x^{k+1}=\frac {(x_t+x_{t-1})}{2}-(1-\gamma_t-\gamma_{t-1} ) \frac{(z_t-z_{t-1})}{2r\mu}
\end{equation}

$x_t-x_{t-1} \leq \epsilon$

$\epsilon > 0$

\begin{equation}\label{testFunction}
\varphi(x) =  0.1\sum_{i=1}^5{i\sin{(10(i+1)x+i)}}+
\begin{cases}
	-4, &0 \leq x < 3.1\\
	10, &3.1 \leq x < 4.6\\
	0, &4.6 \leq x < 7.0\\
	30, &7.0 \leq x < 9.0\\
	0, &9.0 \leq x \leq 10.0
\end{cases}
\end{equation}

$x\in[0,10]$

$r=2.0,\epsilon=0.001$

\begin{figure}[!ht]
	\begin{center}
			\includegraphics[width=0.9\linewidth]{ris_1.jpg}
			\caption{Fig.1}
      \label{ris1}
	\end{center}
\end{figure}

\section{3}

$\varphi(x)$

$\omega \in(x_{i-1},x_i)$

$\mu_i$

$\mu_i$

$(x_{i-1},x_i)$

$\mu_i$

\begin{equation}\label{mu_cond}
\mu(1) \leq \mu(2) \leq ... \leq \mu(m)
\end{equation}

\begin{equation}\label{mu_main_cond}
 \frac{\mu(p)}{\mu(p+1)} \leq Q, 1 \leq p < q(m-2(s+1))
\end{equation}

$Q >1$ and $0<q<1$

$\mu_i$

$p<m-2(s+1)$

$1 \leq p<q(m-2(s+1))$

$\mu_i$

$I=\{i:1 \leq i \leq m,\mu_i=\mu(j),1 \leq j \leq p\}$

$(x_{i-1},x_i)$

$\mu_i$

$(x_{i-1},x_i), i \in I$

\section{4}

$x^i \in (\omega_{i-1},\omega_i ),1 \leq i \leq s+1$

$\Omega=\{\omega_0,…,\omega_{s+1}\}$

$\omega_0=a$ and $\omega_{s+1}=b$

$x^{k+1}, k \geq s+1$

$\{x^1,...,x^k\} \cup \Omega$

\begin{equation}\label{x_cond}
 a=x_0<x_1<...<x_{m-1}<x_m=b,
\end{equation}

$m=s+k+1$

$\gamma_i$

$z_i=\varphi(x_i )$

$ x_i \not\in \Omega$

$\gamma_i=0$

$\mu_i,1 \leq i \leq m$

$0<q<1<Q$

\begin{equation}\label{delta_cond}
\delta_i=
\begin{cases}
	\sign{(z_i - z_{i-1})}, &\text{$i \in I$} \\
	0, &\text{$i \not \in I$}
\end{cases}
\end{equation}

$\delta_i=-1$

$(x_{i-1},x_i ), \delta_i=1$

$\delta_i=0$

$ 0 \leq \gamma_i+\gamma_{i-1}+|\delta_i | \leq 1$

$1 \leq i \leq m$

\begin{equation}\label{mu_new}
\mu=\max\left\{(1-\gamma_i-\gamma_{i-1}-|\delta_i|) \frac {|z_i-z_{i-1}|}{(x_i-x_{i-1})}: 1 \leq i \leq m\}\right\}
\end{equation}

$\mu=0$ $\mu=1$

$(x_{i-1},x_i), 1 \leq i \leq m$

\begin{equation}\label{mu_new}
\begin{gathered}
R(i)=(1+\gamma_i+\gamma_(i-1)+|\delta_i |) \Delta_i+(1-\gamma_i-\gamma_{i-1}-|\delta_i |)\frac{(z_i-z_{i-1} )^2}{(r\mu)^2 \Delta_i } \\
- \frac{2[((1-\gamma_i )(1+\gamma_{i-1} )(1-\delta_i )) z_i+((1+\gamma_i )(1-\gamma_{i-1} )(1+\delta_i )) z_{i-1} ]}{r\mu}
\end{gathered}
\end{equation}

$\mu$ $\Delta_i=x_i-x_{i-1}$

\begin{equation}\label{R}
R(t)=\max\left\{R(i): 1 \leq i \leq m\}\right\}
\end{equation}

\begin{equation}\label{new_x_2}
x^{k+1}=\frac {(x_t+x_{t-1})}{2}-(1-\gamma_t-\gamma_{t-1}- |\delta_t|) \frac{(z_t-z_{t-1})}{2r\mu}
\end{equation}

$x_t-x_{t-1} \leq \epsilon$

$\epsilon > 0$

$r=2.0,\epsilon=0.001,Q=3.0,q=0.3$

\begin{figure}[!ht]
	\begin{center}
			\includegraphics[width=0.9\linewidth]{ris_2.jpg}
			\caption{Fig.2}
      \label{ris2}
	\end{center}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
			\includegraphics[width=0.9\linewidth]{ris_3.jpg}
			\caption{Fig.3}
      \label{ris3}
	\end{center}
\end{figure}

$r=2.0,\epsilon=0.001,Q=3.0,q=0.3$

\section{Results of Numerical Experiments}

\cite{Audet}
\cite{Goldberg}
\cite{Kirkpatrick}
\cite{MatlabOTB}

\begin{equation}\label{seriaFunction}
f(x) =  \sum_{i=0}^4{(j+1)A_j\sin{(5\pi jx+j)}+(j+1)B_j\cos(3\pi jx+j)}, x\in[0,1]
\end{equation}

$A_j,B_j$

$[-6,6]$

$\omega_1,\omega_2,\omega_3,\omega_4$

$[0,0.25), [0.25,0.5), [0.5,0.75), [0.75,1]$

$\delta_1,\delta_2,\delta_3,\delta_4$

$[-50,50]$

\begin{equation}\label{seriaFunction_jump}
\varphi(x) =  f(x)+
\begin{cases}
	\delta_1, &0 \leq x < \omega_1\\
	\delta_2, &\omega_1 \leq x < \omega_2\\
	\delta_3, &\omega_2 \leq x < \omega_3\\
	\delta_4, &\omega_3 \leq x < \omega_4\\
	\delta_1, &\omega_4 \leq x \leq 1.0
\end{cases}
\end{equation}

$x\in[0,1]$

global optimizer $x^*$

$x^k$

$|x^k-x^* | \leq \delta$

$x^*$

$\delta= 10^{-2}$

$\epsilon = 10^{-3}$

$x_0$

 MATLAB Global Optimization Toolbox

$r=2.2$

\begin{table}[h]
	\caption{Results}
	\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline
			Method & Solved & Sr count of iteration & Sr funccount \\
			\hline
			\hline
                                AGS-D & 1000  &  52  &  53 \\
                                \hline
                                SA    &  1000  &  774  &  777  \\
			\hline
			GA    &   999  &  24  &  1290  \\
			\hline
                                DS    &  970  & 38  &  71  \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

$r=3.7,Q=3.0,q=0.3$

\begin{table}[h]
	\caption{Results 2}
	\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline
			Method & Solved & Sr count of iteration & Sr funccount \\
			\hline
			\hline
                                AGS-D & 1000  & 79  &  80 \\
                                \hline
                                SA    &  998  &  765  &  770  \\
			\hline
			GA    &   993  &  25  &  1310  \\
			\hline
                                DS    &  964  & 38  &  71  \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

Word order:

\cite{Sergeyev2013}
\cite{PaulaviciusZilinskas2014}
\cite{Sergeyev2017}
\cite{Horst1995}
\cite{Horst1996}
\cite{Pinter1996}
\cite{Jones2009}

\cite{Evtushenko2009}
\cite{Paulavicius2011}
\cite{Evtushenko2013}
\cite{Strongin2000}

\cite{Moreau2000}

\cite{Batukhtin1993}
\cite{Batukhtin1998}
\cite{Ban2019}

\cite{ZhangXu}
\cite{Audet}

\cite{Goldberg}
\cite{Kirkpatrick}
\cite{MatlabOTB}
